\speculake: Hiding Malware in Speculative Execution

### 2018-08-03 paper/implementation.tex
add values

%TODO: Ian please fill in these numbers
Instead, we
repeat the execution several times and look for the modal value over all
iterations. We measured the
error rate of our implementation as a function of how many redundant iterations
of the same step, and found that 10 redundant iterations resulted in 1 error every
million Turing steps, with the error rate dropping exponentially as iterations
increase. We choose TODO(Ian) iterations as a conservative bound (error rate measured
to be 0), and computed 1 million Turing steps at a rate of TODO(Ian)
steps per second.

>>>>

Instead, we
repeat the execution several times and look for the modal value over all
iterations. We measured the
error rate of our implementation as a function of how many redundant iterations
of the same step, and found that 10 redundant iterations resulted in 1 error every
million Turing steps, with the error rate dropping exponentially as iterations
increase. We choose 11 iterations as a conservative bound (error rate measured
to be 0), and computed 1 million Turing steps at a rate of 1351.75
steps per second.
